parameters

### 2020-02-12 manuscript/drafts/manuscript.Rmd
added a few metrics

# rows to drop
droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
combins <- combins[!droprows, ]
```

ASReview takes the following parameters/arguments:

@@

## Models 
### Naive Bayes 
Naive Bayes assumes all features are independent given the class value. [@Zhang2004]

@@

### Random Forests
A number of decision trees are fit on bootstrapped samples of the original data, 
[@Breiman2001]
RandomForestClassifier from sklearn

@@

### Support Vector Machine

### Logistic Regression

### __Dense Neural Network__

## Query Strategies 
* Max - Choose the most likely samples to be included according to the model
* Uncertainty - choose the most uncertain samples according to the model (i.e. closest to 0.5 probability) [@Lewis1994] 
* Random - randomly selects abstracts with no regard to model assigned probabilities. 
* Cluster - Use clustering after feature extraction on the dataset. Then the highest probabilities within random clusters are sampled

@@

## Balance Strategies

## amount of training data

@@

>>>>

# rows to drop
droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
combins <- combins[!droprows, ]
``` 
# Introduction

## The problem
## Current solutions
Workload savings 30-70 percent, at a loss of 5% of relevant studies [@Omara-Eves2015].

# The software 
ASReview takes the following parameters/arguments:

@@

### Models 
#### Naive Bayes 
Naive Bayes assumes all features are independent given the class value. [@Zhang2004]

@@

#### Random Forests
A number of decision trees are fit on bootstrapped samples of the original data, 
[@Breiman2001]
RandomForestClassifier from sklearn

@@

#### Support Vector Machine

#### Logistic Regression

#### __Dense Neural Network__

### Query Strategies 
* Max - Choose the most likely samples to be included according to the model
* Uncertainty - choose the most uncertain samples according to the model (i.e. closest to 0.5 probability) [@Lewis1994] 
* Random - randomly selects abstracts with no regard to model assigned probabilities. 
* Cluster - Use clustering after feature extraction on the dataset. Then the highest probabilities within random clusters are sampled

@@

### Balance Strategies

### amount of training data

@@

See appendix A for a table containing all 273 combinations.

# Performance metrics
Tradeoff: identifying all relevant papers and reducing workload.

What is more important: recall or precision?

Recall more highly valued than precision.

What about class imbalance?

#### RRF
Amount of relevant references found after having screened a certain percentage of the total number of abstracts.

#### Work saved over sampling (WSS)
Indicates how much time can be saved, at a given level of recall.
WSS is in terms of the percentage of abstracts that don't have to be screened by the researcher. 
Typically, WSS is measured at a recall of 0.95.

$$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall ) $$

#### Raoul
#### Utility? 
#### F-measure 
#### ROC/AUC

# Appendix A - combinations
